A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-06 main.tex
Application of multistage calculi.
Make subsubsections of  section 1.
Wrote the first sentences of each paragraph.

\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
\blue{コードとかはボールドを使ったほうが良いかもしれない。}
\red{Suspicious senetences are colored red.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organization of the Paper}

@@

@@

@@

\red{Besides,} multistage calculi also have a long history of research.
Davis revealed there is Curry-Howard correspondence between a multistage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
However, $\lambda^\circ$ don't have operators for run and CSP.
\red{runはboldかな?}

@@

>>>>

\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
\blue{コードとかはボールドを使ったほうが良いかもしれない。}
\red{Suspicious senetences are colored red.}
%
%
%
\red{Multistage Programming と Multistage Calculus をどう使い分けるか?}
\section{Introduction}

\subsection{Multistage Programming}

\subsubsection{多段階計算とは何か?}

Multistage programming enable us to generate and run fragments of code at runtime.

\subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}

The main application of multistage calculi is program optimization.

\subsubsection{行列計算も高速化できる}

Multistage calculi can also optimize matrices calculation.

\subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}

Generated code is specialized for a given size of matrix and we cannot use it for different sizes.
We call this problem \red{Specialized Code Problem}.

\subsection{Dependent Types}

\subsubsection{依存型とは何か?}

Dependent types are types which is dependent on values.
For example, we can realize vectors with their sizes with them.

\subsubsection{依存型のメリットをサイズ付きのvector, matrixの例を用いて説明する}

The merit of dependent types is guarantee of properties of programs more precisely.

\subsection{Multistage Programming with Dependent Types}

\subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}

We resolve Specialized Code Problem using dependent types.

\subsubsection{Organization of the Paper}

The organization of this paper is following.

@@

% 依存型の歴史

@@

% 依存型の応用

@@

% 多段階計算の歴史

\red{Besides,} multistage calculi also have a long history of research.
Davis revealed there is Curry-Howard correspondence between a multistage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
However, $\lambda^\circ$ don't have operators for run and CSP.
\red{runはboldか? Besidesより適切な接続詞はないのか?}

@@

% 多段階計算の応用

MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
which include filtering in signal processing, matrix-vector product, and DSL compiler.
